Anonymous provision of services via blockchain

### 2022-02-09 main.tex
docs: update

\subsection{Pseudo-anonymous vs anonymous blockchain}

>>>>

\subsection{Pseudo-anonymous vs anonymous blockchain}
Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambigous definitions. Therefore we do not attempt to pick any definion of privacy, rather build on more concrete concept that is anonymity.[[Information Privacy Research]]

Anonymity is a the ability to hide one identity from others. More precisely, the unability to correlate actions performed within the sytem to the identity of the user. Or we can say, that the system guarantee anonimity if for all observers the actions are equally likely to be associated with any user of the system.
However, anonimity is a spectrum rather than dichotomous classification. One method of quantifying level of anonymity is proposed in [[k-anonymity]]. It measure the user's anonymity by the number of other users from whom the user can not be distinguished. Concreatly, the user is *k*-anonymous if his actions are equaly likely associated with *k*-1 other users. The larger *k*, the higher anonimity. The cryptocurrencies that natively support anonymous transactions are [[Monero]] (via [[Confidential Transactions]]) and [[ZCash]] (via [[zkSNARK]]s). There are also techniques that can be deployed on non-anonymous blockchains, they are so-called mixers [[Tornado Cash]], [[CoinJoin]], cite more..., that literaly gather together "anonimimity set" of users that collude together in order to launder the transactions, in such a way that to the outside observer the likelyhood of the sender of each transaction was equiprobable for any user from the anonimity set.

Some systems guarantee pseudonomity rather than anonimity. Pseudonomity, allows uses to hide their real identity behind the pseudonim. Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret. This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges. This makes the anonymity of the user dependent on the security of the IT system. Moreover, some correlations can be infered merely by the analysis of transactions [[Evaluating user privacy in bitcoin]], [[Structure and anonymity of the bitcoin transaction graph]]. Examples of pseudonomous blockchains are [[Bitcoin]] and [[Ethereum]].
